Vectorizing Python Constructs Using Pythran and Boost SIMD

### 2013-11-22 doc/papers/wpmvp14/paper.tex
Intro: first XP

\usepackage{amsmath}
\usepackage{listings}

@@

For instance, the natural solution to Project Euler sixth problem ``Find the
difference between the sum of the squares of the first one hundred natural
numbers and the square of the sum`` can be coded as in
Listing~\ref{lst:euler06-py} in Python and as in Listing~\ref{lst:euler06-c} in
C.

\begin{lstlisting}[language=python, label={lst:euler06-py}, caption={Solution to the Project Euler Sixth Problem in Python}]
def solve();
  r = xrange(1, 101)
  a = sum(r)
  return a * a - sum(i*i for i in r)
\end{lstlisting}

\begin{lstlisting}[language=c, label={lst:euler06-c}, caption={Solution to the Project Euler Sixth Problem in C}]
size_t solve() {
  size_t a = 0, s = 0;
  for(size_t i = 0; i< 101; ++i) {
    a += i;
    s += i*i;
  }
  return a * a - s
}
\end{lstlisting}

>>>>

\usepackage{amsmath}
\usepackage{listings}
\usepackage{hyperref}

@@

For instance, the natural solution to Project Euler sixth problem ``Find the
difference between the sum of the squares of the first one hundred natural
numbers and the square of the sum`` can be coded as in
Listing~\ref{lst:euler06-py} in Python and as in Listing~\ref{lst:euler06-c} in
C. A comparison of the performance of the Python function and the C function
called through the \texttt{ctypes} module shows that the C version runs more
than $\times250$ faster than the Python version. Enabling compiler
auto-vectorization makes the C version $\times400$ faster than the Python
version.~\footnote{To perform more reliable time measurements, \texttt{n} has
    been increased to 100001 instead of 101. The script used to perform the
    measures as well as all other experimental data are available at
\url{https://github.com/serge-sans-paille/pythran/tree/wpmvp14/doc/papers/wpmvp14/experiments}.}

\lstinputlisting[language=python, label={lst:euler06-py}, caption={Solution to the Project Euler Sixth Problem in Python}]{experiments/euler06.py}

\lstinputlisting[language=c, label={lst:euler06-c}, caption={Solution to the Project Euler Sixth Problem in C}]{experiments/euler06.c}
